---
title: "README"
author: "Austin Schwarz"
date: "6/11/2020"
output: html_document
---

The first part of this package get data from 247Sports' Website. It can scrape based on position, state, or commit status. All of these functions can take either a single year or a vector of years. The functions only return the first 50 players of each category, if there are that many. Obviously, for a state like California, there are many more than 50 players, so it'll return the 50 best. But for a recruiting class, like the Penn State recruiting class I scrape below, it should have ~20-30 players.

Here is by position. QBs are divided into dual threat and pro style:
```{r}
dual_threat_qbs <- get_position("dual",2020)
```

Here is by state. State must bee abbreviated. If you want the top players in the country, make state = "USA".
```{r}
nevada <- get_hs_players("NV",2020)
usa <- get_hs_players("USA",2020)
```

Here is by commit status. 
```{r}
penn_state <- get_commits("penn state",2020)
```

The second part of this package gets latitude and longitude of players' hometowns by scraping and then plots them onto an interactive leaflet map. The input here is data.frames created by the previous three functions, which means these two parts of the package are supposed to be used in tandem.

Here is the leaflet map:
```{r}
map_of_players(usa)
```

Each of the data points is clickable with all kinds of information about each players.